\documentclass[aspectratio=169]{beamer}

% Needed packages
\usepackage{hyperref}
\usepackage{listings}
\usepackage{tabularx}

% Use the Fontys theme
\usetheme[lang=en]{Fontys}

\usepackage[backend=bibtex]{biblatex}
\addbibresource{references.bib}


% Title page settings
\title{Neo4j}
\institute{FHTenL}
\author{M. Gorlas, N. Adamavicius}

% Start the document
\begin{document}

% Create title page
\begin{titleframe}
    \titlepage
\end{titleframe}

\begin{frame}
    \frametitle{Roadmap}
    \tableofcontents
\end{frame}

\section{Data model and schema}
% Example frame for itemize
\begin{frame}
    \frametitle{Data model}

    \begin{itemize}
        \item Which data model is used in the DBMS if it’s not relational? Illustrate if necessary (demo). \footfullcite{robinson2015graph} % just an example
        \item Option three
    \end{itemize}

\end{frame}

\begin{frame}
    \frametitle{Database schema}

    \begin{itemize}
        \item Is it necessary or possible to define a database schema? How can that be done (demo)?
    \end{itemize}
\end{frame}

\section{Consistency and Replication}
% Example frame for URL
\begin{frame}
    \frametitle{Consistency}
    
    How is the CAP theorem applied to the DBMS? What type of consistency
is maintained in the system? Can you choose?

\end{frame}

\begin{frame}
    \frametitle{Replication}

    Describe how replication works in the DBMS.
\end{frame}

\section{Security and Performance}

\begin{frame}
    \frametitle{Security}

    \begin{itemize}
        \item Schema-based Security \footfullcite{sbs}
        \item Role-based access control \footfullcite{ac}
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Schema-based Security}
    \begin{itemize}
        \item Protect the nodes and relationships by controling users' ability to traverse and read from different parts of the graph.
        \item Ensures that only authorized users have access to the data they need to protect sensitive data.
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Role-based access control}
    \begin{itemize}
        \item An approach, where you can apply restrictions to roles assigned to users at any level of granularity throughout the graph.
        \item Simplifies the task of assigning permissions and helps ensure that your data is secure.
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Performance}

    Compare the performance of the DBMS with other DBMSs of the same and/or different
    types (recent diagrams, give source, state how and what exactly was measured, be critical)
\end{frame}

\section{Specific use cases and bit of history}

\begin{frame}
    \frametitle{Specific use cases}
    For which kind of use cases is the DBMS specifically good for, and why?
\end{frame}

\begin{frame}
    \frametitle{History}
    Provide some economic information, e.g. market share, history, and any famous case(s)
\end{frame}

\section{Demo}

\begin{frame}
    \frametitle{Demo}
\end{frame}

\end{document}
